Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Add remaining bib data

\bibitem[Acheson(1990)]{Acheson1990}
Acheson, D.
\newblock {\em Elementary Fluid Dynamics}; Oxford University Press: \hl{City, Country,} 1990.

@@

\bibitem[Templin(1974)]{Templin1974}
Templin, R.J.
\newblock \emph{Aerodynamic Performance Theory for the NRC Vertical Axis Wind
 Turbine};
\newblock Technical Report LTR-LA-160; \hl {NRC (Please define)} of Canada: \hl{City, Country,} 1974.

@@

\bibitem[Polagye \em{et~al.}(2013)Polagye, Cavagnaro, and
 Niblick]{Polagye2013b}
Polagye, B.L.; Cavagnaro, R.J.; Niblick, A.L.
\newblock Micropower from tidal turbines.
\newblock In Proceedings of the ASME Fluids Engineering Division Summer Meeting, \hl{City, Country,} \hl{Day Month} 2013.

\bibitem[Bravo \em{et~al.}(2007)Bravo, Tullis, and Ziada]{Bravo2007}
Bravo, R.; Tullis, S.; Ziada, S.
\newblock Performance testing of a small vertical-axis wind turbine.
\newblock In Proceedings of the 21st Canadian Congress of Applied Mechanics
 CANCAM, \hl{City, Country,} \hl{Day Month} 2007.

\bibitem[Bachant and Wosnik(2014)]{Bachant2014}
Bachant, P.; Wosnik, M.
\newblock Reynolds number dependence of cross-flow turbine performance and
 near-wake characteristics.
\newblock In Proceedings of the 2nd Marine Energy Technology Symposium METS2014, \hl{City, Country,} \hl{Day Month} 2014.

@@

\bibitem[Jacobs and Sherman(1937)]{Jacobs1937}
Jacobs, E.N.; Sherman, A.
\newblock \emph{Airfoil Section Characteristics as Affected by Variation of the
 Reynolds Number};
\newblock Technical Report; National Advisory Committee for Aeronautics: \hl{City, Country}, 1937.

@@

\bibitem[Bousman(2000)]{Bousman2000-evaluation}
Bousman, W.G.
\newblock Evaluation of airfoil dynamic stall characteristics for
 maneuverability.
\newblock In Proceedings of the 26th {E}uropean Rotorcraft Forum, \hl{City, Country,} \hl{Day Month} 2000.

@@

\bibitem[Neary \em{et~al.}(2014)Neary, Previsic, Jepsen, Lawson, Yu, Copping,
 Fontaine, Hallett, and Murray]{Neary2014}
Neary, V.S.; Previsic, M.; Jepsen, R.A.; Lawson, M.J.; Yu, Y.H.; Copping, A.E.;
 Fontaine, A.A.; Hallett, K.C.; Murray, D.K.
\newblock \emph{Methodology for Design and Economic Analysis of Marine Energy
 Conversion ({MEC}) Technologies};
\newblock Technical Report SAND2014-9040; Sandia National Laboratories: \hl{City, Country}, 2014.

\bibitem[Cavagnaro and Polagye(2014)]{Cavagnaro2014}
Cavagnaro, R.; Polagye, B.
\newblock An evaluation of blockage corrections for a helical cross-flow
 turbine.
\newblock In~Proceedings of the 3rd Oxford Tidal Energy Workshop, \hl{City, Country,} \hl{Day Month} 2014.

@@

\bibitem[Bachant and Wosnik(2016)]{Bachant2015-RVAT-Re-dep-data} Bachant, P.;
Wosnik, M. \newblock {UNH-RVAT} {R}eynolds Number Dependence Experiment: Reduced
Dataset and Processing Code. \newblock Fig\textbf{share}. Available online:
\url{http://dx.doi.org/10.6084/m9.figshare.1286960} (accessed on 22 January
2015).

>>>>

\bibitem[Acheson(1990)]{Acheson1990} Acheson, D. \newblock {\em Elementary Fluid
    Dynamics}; Oxford University Press: Oxford, UK, 1990.

@@

\bibitem[Templin(1974)]{Templin1974} Templin, R.J. \newblock \emph{Aerodynamic
    Performance Theory for the NRC Vertical Axis Wind Turbine}; \newblock Technical
Report LTR-LA-160; National Research Council Canada: Ottawa, Canada 1974.

@@

\bibitem[Polagye \em{et~al.}(2013)Polagye, Cavagnaro, and Niblick]{Polagye2013b}
Polagye, B.L.; Cavagnaro, R.J.; Niblick, A.L. \newblock Micropower from tidal
turbines. \newblock In Proceedings of the ASME Fluids Engineering Division
Summer Meeting, Incline Village, NV, USA, 7--11 July 2013.

\bibitem[Bravo \em{et~al.}(2007)Bravo, Tullis, and Ziada]{Bravo2007} Bravo, R.;
Tullis, S.; Ziada, S. \newblock Performance testing of a small vertical-axis
wind turbine. \newblock In Proceedings of the 21st Canadian Congress of Applied
Mechanics CANCAM, Toronto, Ontario, Canada, 3--7 June 2007.

\bibitem[Bachant and Wosnik(2014)]{Bachant2014} Bachant, P.; Wosnik, M.
\newblock Reynolds number dependence of cross-flow turbine performance and
near-wake characteristics. \newblock In Proceedings of the 2nd Marine Energy
Technology Symposium METS2014, Seattle, WA, USA, 15--18 April 2014.

@@

\bibitem[Jacobs and Sherman(1937)]{Jacobs1937} Jacobs, E.N.; Sherman, A.
\newblock \emph{Airfoil Section Characteristics as Affected by Variation of the
    Reynolds Number}; \newblock Technical Report; National Advisory Committee for
Aeronautics: Langley Field, VA, United States, 1937.

@@

\bibitem[Bousman(2000)]{Bousman2000-evaluation} Bousman, W.G. \newblock
Evaluation of airfoil dynamic stall characteristics for maneuverability.
\newblock In Proceedings of the 26th {E}uropean Rotorcraft Forum, The Hague,
Netherlands, 26--29 September 2000.

@@

\bibitem[Neary \em{et~al.}(2014)Neary, Previsic, Jepsen, Lawson, Yu, Copping,
Fontaine, Hallett, and Murray]{Neary2014} Neary, V.S.; Previsic, M.; Jepsen,
R.A.; Lawson, M.J.; Yu, Y.H.; Copping, A.E.; Fontaine, A.A.; Hallett, K.C.;
Murray, D.K. \newblock \emph{Methodology for Design and Economic Analysis of
    Marine Energy Conversion ({MEC}) Technologies}; \newblock Technical Report
SAND2014-9040; Sandia National Laboratories: Albuquerque, NM, USA, 2014.

\bibitem[Cavagnaro and Polagye(2014)]{Cavagnaro2014} Cavagnaro, R.; Polagye, B.
\newblock An evaluation of blockage corrections for a helical cross-flow
turbine. \newblock In~Proceedings of the 3rd Oxford Tidal Energy Workshop,
Oxford, UK, 7--8 April 2014.

@@

\bibitem[Bachant and Wosnik(2016)]{Bachant2015-RVAT-Re-dep-data} Bachant, P.;
Wosnik, M. \newblock {UNH-RVAT} {R}eynolds Number Dependence Experiment: Reduced
Dataset and Processing Code. \newblock Fig\textbf{share}. Available online:
\url{http://dx.doi.org/10.6084/m9.figshare.1286960} (accessed on 22 January
2016).
